Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
Update paper.tex

The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

% \linespread{1.1}
\begin{figure}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{fig:assemble-example-encoding}
\end{figure}
% \linespread{1.0}

@@

Since we want to get 0/1-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

@@

We train each classifer with $1500$ iterations with a batch size $200$. The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$. We only train the pruned model i.e. weights of the pruned channels will remain zero.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}

>>>>

Table~\ref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

% \linespread{1.1}
\begin{table}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{tab:assemble-example-encoding}
\end{table}
% \linespread{1.0}

@@

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

@@

We train each classifer with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
\end{table}

\paragraph{Verifying Result.}By combining the 0/1-results of the four classifiers, we can determine the class label unqiuely of one test sample.
For example, if the result of classifer-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}

The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}. We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.

\begin{table}[!htp]
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
\end{table}
